How residence time constrains diversity

### 2015-06-01 analyses/ResTime.Rmd

```{r, results = 'hide', message=FALSE}
#install.packages("vegan") 
#instead, use try("vegan")
require("vegan") 
```

@@

```{r}
par(mfrow=c(2, 2))
x <- log(sim.data$TracerParticle_ResTime)
N <- log(sim.data$TotalAbundance)
plot(x, N, xlab="Particle Residence Time", 
     ylab="Total Abundance", 
     main = "N vs. Tau", col='SteelBlue')

x <- log(sim.data$MicrobeCell_ResTime)
plot(x, N, xlab="Cell Residence Time", 
     ylab="Total Abundance", 
     main = "N vs. Tau", col='darkorchid4')

x <- log(sim.data$TracerParticle_ResTime)
S <- log(sim.data$SpeciesRichness)
plot(x, S, xlab="Particle Residence Time", 
     ylab="Total Abundance", 
     main = "S vs. Tau", col='SteelBlue')

x <- log(sim.data$MicrobeCell_ResTime)
plot(x, S, xlab="Cell Residence Time", 
     ylab="Total Abundance", 
     main = "S vs. Tau", col='darkorchid4')
```

>>>>

```{r, results = 'hide', message=FALSE}
#install.packages("vegan") 
require("vegan") 
```

@@

```{r}
par(mfrow=c(2, 2))
tau <- log(sim.data$TracerParticle_ResTime)
N <- log(sim.data$TotalAbundance)
plot(tau, N, xlab="Particle Residence Time", 
     ylab="Total Abundance", 
     main = "N vs. Tau", col='SteelBlue')

tau <- log(sim.data$MicrobeCell_ResTime)
plot(tau, N, xlab="Cell Residence Time", 
     ylab="Total Abundance", 
     main = "N vs. Tau", col='darkorchid4')

tau <- log(sim.data$TracerParticle_ResTime)
S <- log(sim.data$SpeciesRichness)
plot(tau, S, xlab="Particle Residence Time", 
     ylab="Species Richness", 
     main = "S vs. Tau", col='SteelBlue')

tau <- log(sim.data$MicrobeCell_ResTime)
plot(tau, S, xlab="Cell Residence Time", 
     ylab="Species Richness", 
     main = "S vs. Tau", col='darkorchid4')
```

```{r}
par(mfrow=c(2, 2))
tau <- log(sim.data$MicrobeCell_ResTime)
N <- sim.data$TotalAbundance
plot(tau, log(N), xlab="Cell Residence Time", 
     ylab="Total Abundance", 
     col='SteelBlue')

S <- sim.data$SpeciesRichness
plot(tau, log(S), xlab="Cell Residence Time", 
     ylab="Species Richness", 
     col='darkorchid4')

E <- sim.data$Evar
plot(tau, E, xlab="Cell Residence Time", 
     ylab="Species Evenness", 
     col='SteelBlue')

avg.ab <- N/S
plot(tau, avg.ab, xlab="Cell Residence Time", 
     ylab="Average Abundance", 
     col='darkorchid4')
```

```{r}
par(mfrow=c(2, 2))
tau <- log(sim.data$MicrobeCell_ResTime)
BP <- sim.data$BergerParker
plot(tau, BP, xlab="Cell Residence Time", 
     ylab="Berger-Parker", 
     col='SteelBlue')

SimpD <- sim.data$InvSimpDiversity
plot(tau, SimpD, xlab="Cell Residence Time", 
     ylab="Simpsons Diversity (1/D)", 
     col='darkorchid4')

Skew <- sim.data$Skew
plot(tau, Skew, xlab="Cell Residence Time", 
     ylab="Skewness", 
     col='SteelBlue')

Nmax <- sim.data$Nmax
plot(tau, log(Nmax), xlab="Cell Residence Time", 
     ylab="Nmax", 
     col='darkorchid4')
```
